Solution

Package used
```{r}
options(java.parameters = c("-XX:+UseConcMarkSweepGC", "-Xmx8192m"))
require(xlsx)
require(sqldf)
require(ggplot2)
require(mclust)
require(rpart)
require(rpart.plot)
```

data input
```{r}
getwd()
data <- read.xlsx("C:/Users/OWNER/Desktop/ITP4475_student_project/sale_Data.xlsx", sheetIndex = 2)
info <- read.xlsx("C:/Users/OWNER/Desktop/ITP4475_student_project/sale_Data.xlsx", sheetIndex = 1)
```

Data Observation / Cleansing
```{r}
#prove there are 70680 sales records
nrow(data)

#prove product name in both dataset are synchronized
DataProducts <- unique(data$商品)
InfoProducts <- unique(info$商品)

DataMissing <- setdiff(InfoProducts, DataProducts)
InfoMissing <- setdiff(DataProducts, InfoProducts)

DataMissing
InfoMissing

#prove product_price = actual paid
pricediff = setdiff(data$应付金额, data$实际金额)
pricediff

#list any uncleaned data for cleansing if necessary
colSums(is.na(data))
data <- na.omit(data)


```

Merge Data
```{r}
merged_data <- merge(x = data, y = info, by = "商品", all.x = TRUE)
```

Mission 1.1 According to the merged dataset, suppose each location only have one vendor machine. Extract the Sales record from the merged dataset and store the data separately based on the Vendor machine location "A", "B", "C", "D", "E".
```{r}
loc_A <- merged_data[merged_data$地点 == "A", ]
loc_B <- merged_data[merged_data$地点 == "B", ]
loc_C <- merged_data[merged_data$地点 == "C", ]
loc_D <- merged_data[merged_data$地点 == "D", ]
loc_E <- merged_data[merged_data$地点 == "E", ]
```

Mission 1.2 Calculate each vending machine’s sales revenue and number of orders for April 2017, and also compute the overall total sales revenue and total number of orders across all vending machines. Display the results in a table within the report.
```{r}
april_data <- merged_data[merged_data$支付时间 >= "2017-04-01 00:00:00" & 
                          merged_data$支付时间 <= "2017-04-30 23:59:59", ]

locations <- c("A", "B", "C", "D", "E")
result_table <- data.frame(地点 = locations, 订单数 = 0, 销售额 = 0)

for(i in 1:5) {
  loc <- locations[i]
  sub_data <- april_data[april_data$地点 == loc, ]
  
  result_table$订单数[i] <- length(unique(sub_data$订单号))
  result_table$销售额[i] <- sum(sub_data$实际金额, na.rm = TRUE)
}

total_row <- data.frame(地点 = "总计", 
                        订单数 = sum(result_table$订单数), 
                        销售额 = sum(result_table$销售额))

final_table <- rbind(result_table, total_row)
```

Mission 1.3 Summaries the monthly average Revenue of each Vendor machine and also it is daily average Sale volume.
```{r}
agg_data$地点 <- factor(agg_data$地点, levels = c("A", "B", "C", "D", "E"))
agg_data$月份 <- as.numeric(agg_data$月份)
final_list <- agg_data[order(agg_data$地点, agg_data$月份), ]
print(final_list)



merged_data$日期 <- as.numeric(format(merged_data$支付时间, "%d"))
daily_volume_list <- aggregate(订单号 ~ 地点 + 日期, data = merged_data, FUN = length)
colnames(daily_volume_list) <- c("地点", "日期", "每日销量")
final_daily_list <- daily_volume_list[order(daily_volume_list$地点, daily_volume_list$日期), ]
print(final_daily_list)
```

Mission2.1 visualise the top 5 sale product in June 2017 using bar chart
```{r}
june_data <- sqldf("
    SELECT * 
    FROM merged_data 
    WHERE strftime('%Y-%m', 支付时间) = '2017-06'
")

top5 <- sqldf("
    SELECT 商品 AS Product, 
           SUM(实际金额) AS Total_Revenue,
           COUNT(*) AS Quantity
    FROM june_data
    GROUP BY 商品
    ORDER BY Total_Revenue DESC
    LIMIT 5
")

ggplot(top5, aes(x = reorder(Product, Total_Revenue), y = Total_Revenue)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 5 Selling Products in June 2017",
       x = "Product Name", 
       y = "Total Revenue (HKD)") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"))
```

Mission 2.2 visualise all vendor machine revenue trend in monthly basis and also its growth rate in bar chart.
```{r}
monthly <- sqldf("
    SELECT strftime('%Y-%m', 支付时间) AS Month,
           SUM(实际金额) AS Total_Revenue
    FROM merged_data
    GROUP BY strftime('%Y-%m', 支付时间)
    ORDER BY Month
")

monthly$Growth_Rate <- NAreal

for(i in 2:nrow(monthly)) {
  if(!is.na(monthly$Total_Revenue[i-1]) && monthly$Total_Revenue[i-1] != 0) {
    monthly$Growth_Rate[i] <- (monthly$Total_Revenue[i] - monthly$Total_Revenue[i-1]) / 
                              monthly$Total_Revenue[i-1] * 100
  }
}

ggplot(monthly, aes(x = Month, y = Total_Revenue, group = 1)) +
  geom_line(color = "blue", size = 1.2) +
  geom_point(color = "blue", size = 3) +
  labs(title = "Monthly Revenue Trend (All Machines)",
       x = "Month", 
       y = "Total Revenue (HKD)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(monthly, aes(x = Month, y = Growth_Rate)) +
  geom_bar(stat = "identity", 
           fill = ifelse(is.na(monthly$Growth_Rate), "grey", 
                         ifelse(monthly$Growth_Rate >= 0, "darkgreen", "red"))) +
  labs(title = "Monthly Revenue Growth Rate (%)",
       x = "Month", 
       y = "Growth Rate (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Mission2.3 plot margin revenue proportion for each vendor machine. Suppose the margin revenue rate of beverage and non-beverage is 25% and 20% respectively.
```{r}

```

Mission 2.4 - plot the total revenue of each machines in April 2027 by bubble chart
```{r}

```

Mission 2.5 - plot the revenue of Vendor machine C in June, July, and August and summmarise the data by heatmap graph.
```{r}

```
Mission 3.1
Use any machine learning approach to auto labelling the salse status of each brevage products in each Vendor machine. There are three types of labels : unsaleable, normal, trending. In which, unsaleable means the salse status was uncertain, and normal means there is no observable sale pattern, treding mean the sale is good. 

```{r}
beverage_data <- subset(merged_data, 大类 == "饮料")
revenue_table <- aggregate(实际金额 ~ 商品, data = beverage_data, FUN = sum)
frequency_table <- aggregate(订单号 ~ 商品, data = beverage_data, FUN = length)
product_metrics <- merge(revenue_table, frequency_table, by = "商品")
colnames(product_metrics) <- c("Product", "Revenue", "Frequency")

scaled_data <- scale(product_metrics[, c("Revenue", "Frequency")])
set.seed(123)
kmeans_result <- kmeans(scaled_data, centers = 3)
product_metrics$Group <- kmeans_result$cluster

product_metrics$Status <- "Normal"
product_metrics$Status[product_metrics$Group == 1] <- "Unsaleable"
product_metrics$Status[product_metrics$Group == 2] <- "Trending"
product_metrics$Status[product_metrics$Group == 3] <- "Normal"

location_map <- unique(beverage_data[, c("商品", "地点")])

final_report <- merge(location_map, product_metrics[, c("Product", "Status")],  by.x = "商品", by.y = "Product")

colnames(final_report) <- c("商品名称", "销售地点", "商品分类")
final_report <- final_report[order(final_report$商品名称), ]

print(final_report)
```

Mission 3.2  Use any machine learning approach to classify the sale segnments of different types of product category by the relationship of the Category total Revenue.
```{r}

```
